---
title: "Welcome!"
subtitle: "<br><br> Tidy up your models"
author: "[datasciencebox.org](https://datasciencebox.org/)"
date: "Mine Çetinkaya-Rundel and Debbie Yuster"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "slides.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      highlightStyle: solarized-light
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 8, 
  fig.asp = 0.618,
  out.width = "60%",
  fig.align = "center",
  dpi = 300
  )

ggplot2::theme_set(ggplot2::theme_minimal(base_size = 16))

library(xaringanExtra)
xaringanExtra::use_panelset()
```

layout: true
  
<div class="my-footer">
<span>
<a href="https://datasciencebox.org" target="_blank">INSERT LINK</a>
</span>
</div> 

---

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emo)
```

## Welcome

- Introductions...
- Useful links

TO DO: Need to update hex for logo for workshop...

---

class: middle

# High level view: tidymodels

---

## With basic model fit (lm) alone, no advantage

Not necessarily better way to do any linear model, better as a framework in general

---

## 	Syntax side by side, tidymodels more complicated -- debbie

---

## Preprocess training and testing data together, recipes as a big picture

---

## Split into training/testing first

---

class: middle

# Case study 1: Linear, simple...

---

MLR example without recipes

- fit model
- prediction
- breakout room: 10 min
		
---

class: middle

# Case study 2: Logistic, more complex...

---

cross validation, autoplot

---

class: middle

# Wrap up

---

## What about inference?

---

## Resources from dsbox

---

class: center, middle

.hand[thank you!]

TO DO: ADD LINKS AGAIN

