---
title: "A more complex logistic model"
output: github_document
---

## Load packages

```{r message = FALSE}
library(openintro)
library(tidyverse)
library(tidymodels)
```

## Take a peek at the data

```{r}
email
```

## Predicting spam

```{r spam-mlr, results = "hide"}
logistic_reg() %>%
  set_engine("glm") %>%
  fit(spam ~ ., data = email, family = "binomial") %>%
  tidy()
```

## Performing the split

```{r}
# Fix random numbers by setting the seed 
# Enables analysis to be reproducible when random numbers are used 
set.seed(1116)

# Put 80% of the data into the training set 
email_split <- initial_split(email, prop = 0.80)

# Create data frames for the two sets:
train_data <- training(email_split)
test_data  <- testing(email_split)
```


## Peek at the split

```{r}
glimpse(train_data)
```

```{r}
glimpse(test_data)
```


## Feature engineering

- We prefer simple models when possible, but **parsimony** does not mean sacrificing accuracy (or predictive performance) in the interest of simplicity

--
- Variables that go into the model and how they are represented are just as critical to success of the model

--
- **Feature engineering** allows us to get creative with our predictors in an effort to make them more useful for our model (to increase its predictive performance) 


## Initiate a recipe

```{r initiate-recipe}
email_rec <- recipe(
  spam ~ .,          # formula
  data = train_data  # data to use for cataloguing names and types of variables
  )

summary(email_rec)
```


## Remove certain variables

```{r}
email_rec <- email_rec %>%
  step_rm(from, sent_email)

email_rec
```


## Feature engineer date

```{r}
email_rec <- email_rec %>%
  step_date(time, features = c("dow", "month")) %>%
  step_rm(time)

email_rec
```


## Discretize numeric variables

```{r}
email_rec <- email_rec %>%
  step_cut(cc, attach, dollar, breaks = c(0, 1)) %>%
  step_cut(inherit, password, breaks = c(0, 1, 5, 10, 20))

email_rec
```


## Create dummy variables

```{r}
email_rec <- email_rec %>%
  step_dummy(all_nominal(), -all_outcomes())

email_rec
```


## Remove zero variance variables

Variables that contain only a single value

```{r}
email_rec <- email_rec %>%
  step_zv(all_predictors())

email_rec
```


## All in one place

```{r}
email_rec <- recipe(spam ~ ., data = email) %>%
  step_rm(from, sent_email) %>%
  step_date(time, features = c("dow", "month")) %>%               
  step_rm(time) %>%
  step_cut(cc, attach, dollar, breaks = c(0, 1)) %>%
  step_cut(inherit, password, breaks = c(0, 1, 5, 10, 20)) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())

email_rec
```


## Define model

```{r}
email_mod <- logistic_reg() %>% 
  set_engine("glm")

email_mod
```


## Define workflow


```{r}
email_wflow <- workflow() %>% 
  add_model(email_mod) %>% 
  add_recipe(email_rec)

email_wflow
```


## Fit model to training data

```{r warning = FALSE}
email_fit <- email_wflow %>% 
  fit(data = train_data)

tidy(email_fit)
```

## Make predictions for test data

```{r}
email_pred <- predict(email_fit, test_data, type = "prob") %>% 
  bind_cols(test_data) 

email_pred
```


## Evaluate the performance

```{r roc}
email_pred %>%
  roc_curve(
    truth = spam,
    .pred_1,
    event_level = "second"
  ) %>%
  autoplot()
```


## Evaluate the performance

```{r}
email_pred %>%
  roc_auc(
    truth = spam,
    .pred_1,
    event_level = "second"
  )
```
